\bf Calendar-based graphics for visualizing people's daily schedules

### 2020-01-08 calendar-vis.Rmd
ready for production

authors:
- name: Earo Wang
  affiliation: Monash University & CSIRO Data61
  email: earo.wang@monash.edu

@@

Figure \@ref(fig:hod) shows energy consumption against time of day, separately by weekday and weekend. Household 1 is an early riser, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning on when they get home from work and keep it operating until midnight, evident from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for household 2 indicates that air conditioning may run continuously for some periods, consuming twice the energy as household 1. A third peak occurs around 15 for household 3 only, likely coinciding when the children arrive home from school. They also have a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 18 on weekdays. Figures \@ref(fig:hod), part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

>>>>

authors:
- name: Earo Wang
  affiliation: The University of Auckland, Monash University, CSIRO Data61
  email: earo.wang@monash.edu

@@

Figure \@ref(fig:hod) shows energy consumption against time of day, separately by weekday and weekend. Household 1 is an early riser, starting their day before 6:00 and going back home around 18:00 on weekdays. They switch air conditioning on when they get home from work and keep it operating until midnight, evident from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for household 2 indicates that air conditioning may run continuously for some periods, consuming twice the energy as household 1. A third peak occurs around 15:00 for household 3 only, likely coinciding when the children arrive home from school. They also have a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 18 on weekdays. Figures \@ref(fig:hod), part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

# Supplementary Materials {-}
The supplementary files include code and datasets used in this article. More is available at <https://github.com/earowang/paper-calendar-vis>.

### 2020-01-08 calendar-vis.tex
ready for production

  \author{
        Earo Wang \\
    Monash University \& CSIRO Data61\\
     and \\     Dianne Cook \\
    Monash University\\
     and \\     Rob J Hyndman \\
    Monash University\\
      }
  \maketitle
} \fi

@@

\caption{Google map of the Melbourne city area, grey dots indicate sensor locations. The three locations highlighted will be analyzed in the paper: the State Library is a public library; Flagstaff Station is a train station, closed on non-work days; Birrarung Marr is an outdoor park hosting many cultural and sports events.}\label{fig:ped-map}
\end{figure}

@@

Then the final coordinates for making the calendar plots of the pedestrian sensor data is given by:
\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  \label{eq:final}
\end{equation}

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by weekday and weekend. Household 1 is an early riser, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning on when they get home from work and keep it operating until midnight, evident from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for household 2 indicates that air conditioning may run continuously for some periods, consuming twice the energy as household 1. A third peak occurs around 15 for household 3 only, likely coinciding when the children arrive home from school. They also have a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 18 on weekdays. Figures \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

>>>>

  \author{
        Earo Wang \\
    The University of Auckland, Monash University, CSIRO Data61\\
     and \\     Dianne Cook \\
    Monash University\\
     and \\     Rob J Hyndman \\
    Monash University\\
      }
  \maketitle
} \fi

@@

\caption{Google map of the Melbourne city area, gray dots indicate sensor locations. The three locations highlighted will be analyzed in the paper: the State Library is a public library; Flagstaff Station is a train station, closed on non-work days; Birrarung Marr is an outdoor park hosting many cultural and sports events.}\label{fig:ped-map}
\end{figure}

@@

Then the final coordinates for making the calendar plots of the pedestrian sensor data are given by:
\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  \label{eq:final}
\end{equation}

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by weekday and weekend. Household 1 is an early riser, starting their day before 6:00 and going back home around 18:00 on weekdays. They switch air conditioning on when they get home from work and keep it operating until midnight, evident from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for household 2 indicates that air conditioning may run continuously for some periods, consuming twice the energy as household 1. A third peak occurs around 15:00 for household 3 only, likely coinciding when the children arrive home from school. They also have a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 18 on weekdays. Figures \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

@@

\hypertarget{supplementary-materials}{%
\section*{Supplementary Materials}\label{supplementary-materials}}
\addcontentsline{toc}{section}{Supplementary Materials}

The supplementary files include code and datasets used in this article. More is available at \url{https://github.com/earowang/paper-calendar-vis}.
